\documentclass[11pt,a4paper,roman]{moderncv}       

\moderncvstyle{banking}                            
\moderncvcolor{blue}                                
\nopagenumbers{}                                  


\usepackage[scale=0.8, top=0.5cm, bottom=1cm, left=1cm, right=1cm]{geometry}

% personal data
\name{Milad}{Teimouri}
\address{Software Engineer}
  
\newcommand*{\customcventry}[7][.23em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcventry}[7][.23em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-25mm}

\begin{center}
\begin{tabular}{ c c c c }
  \faEnvelopeO\enspace milad72t@gmail.com & 
  \faMapMarker\enspace Tehran, Iran &
  Profiles:    
\href{https://www.linkedin.com/in/milad-teimouri-909a9872}{\faLinkedin} 
 \href{https://stackoverflow.com/users/4477569/milad-teimouri}{\faStackOverflow}
 \href{https://github.com/milad72t}{\faGithub}
 \href{https://www.goodreads.com/user/show/82884162-milad}{\faBook} 
\end{tabular}
\newline
\end{center}

\section{SUMMARY}
\begin{minipage}{\maincolumnwidth}%
  \small{
      \begin{itemize}
      I am a software engineer with over six years of experience in e-commerce and billing companies. Experienced in migrating from monolithic to microservices and familiar with the microservices pattern. My expertise lies in PHP, SQL, and NoSQL, and I am enthusiastic about learning and utilizing my skills to develop innovative and efficient solutions.
    \end{itemize}}%
\end{minipage}%
}

\section{EXPERIENCES}
{\customcventry{October  2020 -  Present}{Senior Software Engineer - Platform team}{\href{https://about.digikala.com/en/home/}{Digikala}}{+2.5 yrs}{}
{\begin{itemize}
  \item \href{https://www.linkedin.com/company/digikala/about/}{Digikala Group} is the largest e-commerce platform in the Middle East with +40M visitors and +5M monthly orders.
        \item As a member of the platform(core) team, engaged in providing the infrastructure for migrating to microservices that support 20k RPS by bringing new technologies and developing our customized framework.
      \item Innovated a CQRS service for products that handle more than 5K RPS.
          \item Configured and integrated the Apache APISIX gateway that handles 10k requests as the entry point to more than 50 services.
  \item Rewrote shopping APIs and refactor legacy codes of \href{https://www.digikala.com/}{digikala.com} resulting in a 40\% reduction in resource requests.
  \item Designed \& Developed social e-commerce called \href{https://www.adsoftheworld.com/campaigns/digikala-magnet}{Magnet} which is like Instagram, and currently has over 1 million users and \textasciitilde100k posts created per month.
  \item Participated in onboarding new joiners, hiring process, and revising team structure.
\item Main used technologies: \textbf{PHP}, \textbf{Symfony}, \textbf{Kafka}, \textbf{MySQL}, \textbf{Redis}, \textbf{Elasticsearch} \textbf{Kubernetes}, \textbf{MongoDB}, \textbf{APISIX}
\end{itemize}
}


{\customcventry{September 2017 - October 2020}{Backend Software Engineer}{\href{https://www.linkedin.com/company/andishe-computer/}{Andishe Computer}}{3 yrs}{}
{\begin{itemize}
  \item Launched a billing system that is used by electricity Companies that handles the data of over 10M Power subscribers from all over the country
  \item Created subscriber surveillance and bill payment system that has all energy subscriber's data intended to remove bill papers \href{https://bargheman.com/}{(bargheman.com)}
  \item Structured an automated payment processing system, that gathers financial data from different banks (\textasciitilde2k documents per day) to transmit them to each power distribution and generate financial reports, which removed the need for human work.
\item Main used technologies: \textbf{Laravel}, \textbf{SQLServer}, \textbf{Docker}, \textbf{MongoDB}, \textbf{Redis}, \textbf{Python}, \textbf{C++}
\end{itemize}
}

{\customcventry{April 2017 - September 2017}{Backend Software Engineer}{Behpardaz Pishro}{6 mth}{}
{\begin{itemize}
  \item Completed a system ordered by the Ministry of Power for gathering information about 32M subscribers of electricity from all over the country, generating reports on the data.
\item Main used technologies: \textbf{Laravel}, \textbf{Oracle}, \textbf{MongoDB}
\end{itemize}
}



\section{SKILLS}
\begin{minipage}{\maincolumnwidth}%
  \small{
      \begin{itemize}
                \item Proficient  in \textbf{PHP}
          \item Proficient in \textbf{relational databases} (\textbf{SQL}) and
          \textbf{Database Design}
          \item Experienced with \textbf{Microservices} patterns (\textbf{API-GW}, \textbf{SAGA}, \textbf{CQRS}, \textbf{Event Sourcing})
          \item Experienced with \textbf{NoSQL} databases (\textbf{Redis}, \textbf{MongoDB}, \textbf{Elasticsearch}, \textbf{Memcached})
        \item Experienced with \textbf{Docker}, \textbf{Kubernetes}, 
        \textbf{Kafka} and \textbf{Git}
          \item Experienced with \textbf{Python}, \textbf{Golang},  and \textbf{C++}
  \item Experienced with  \textbf{Linux} and Server maintenance
    \end{itemize}}%
\end{minipage}%
      
\section{EDUCATION}
{\customcventry{2016-2018}{Master of Computer Networks engineering - Second Rank, 17.89 GPA}{\href{https://www.linkedin.com/school/iran-university-of-science-and-technology/}{Iran University of Science and Technology}}{}{}{}}

{\customcventry{2012-2016}{Bachelor of Computer engineering - Third Rank, 16.85 GPA}{\href{https://www.linkedin.com/school/iran-university-of-science-and-technology/}{Iran University of Science and Technology}}{}{}{}}
}
}

\end{document}

